Roster Review (Generic)

### 2019-06-20 rosterReview_generic.Rmd
A few days of lineup retrieval, a few bug fixes. Prepping reaction to rival team trade

```{r}
force <- TRUE
force_all <- TRUE
batter_file <- "temp/FanGraphs Leaderboard.csv"
pitcher_file <- "temp/FanGraphs Leaderboard (1).csv"

if (force_all && (batter_file %>% is.null() || pitcher_file %>% is.null())) {
  stop("Need projection files to force a recalc")
} else {
  rosters <- load_players_with_projections(force, 
                                           force_all, 
                                           batter_file, 
                                           pitcher_file)
}

@@

rosters %>% 
  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 2)) %>% 
  arrange(zar %>% desc) %>% 
  select(name_full, positions, type, zar) %>% 
  View()
```

@@

rosters_by_position %>% 
  select(team, manager, name_full, position, zar, pos_zar) %>% 
  View()

@@

```{r}
# TODO find way to wrap these three views into one
rosters %>% 
  filter(grepl("Plouffe|Nuts",team)) %>% 
  select(team, manager, name_full, display_position, zar, positions) %>% 
  arrange(zar %>% desc) %>% 
  View()
  # mutate(zar = janitor::round_half_up(zar)) %>% 
  # write_csv("data/tradeReview_20190423.csv")

rosters %>% 
  filter(grepl("Plouffe|Nuts",team)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
  coord_flip() -> tv

>>>>

```{r}
force_fetch <- TRUE
force_join <- TRUE
batter_file <- "temp/FanGraphs Leaderboard.csv"
pitcher_file <- "temp/FanGraphs Leaderboard (1).csv"

if (force_fetch && (batter_file %>% is.null() || pitcher_file %>% is.null())) {
  stop("Need projection files to force a recalc")
} else {
  rosters <- load_players_with_projections(force_fetch, 
                                           force_join, 
                                           batter_file, 
                                           pitcher_file)
}

@@

rosters %>% 
  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 2)) %>% 
  arrange(zar %>% desc) %>% 
  mutate(zar = zar %>% round(digits=1)) %>% 
  select(team, name_full, positions, type, zar) %>% 
  View("Available Free Agents")
```

@@

rosters_by_position %>% 
  select(team, manager, name_full, position, zar, pos_zar) %>% 
  # filter(position %in% c('SP','RP')) %>% 
  filter(grepl("Plouffe",team)) %>% 
  arrange(pos_zar %>% desc) %>%
  mutate(pos_zar = pos_zar %>% round(1),
         zar = zar %>% round(1)) %>% 
  View("ZAR by Position")

@@

```{r}
# TODO find way to wrap these three views into one
rosters %>% 
  filter(grepl("Plouffe|Bump",team)) %>% 
  select(team, manager, name_full, display_position, zar, positions) %>% 
  arrange(zar %>% desc) %>% 
  mutate(zar = zar %>% round(1)) %>% 
  View("Trade Partner")
  # mutate(zar = janitor::round_half_up(zar)) %>% 
  # write_csv("data/tradeReview_20190423.csv")

rosters %>% 
  filter(grepl("Plouffe|Bump",team)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
  coord_flip() -> tv
